### 2024-04-22 texts/paper_closing.tex
some more testing, just freely writing

% Created 2024-04-16 di 12:30
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon Apr 15 11:30:07 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 275 & 0.574 &   0.593 &   0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.159 &   0.169 &   0.37 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.267 &   0.238 &   0.43 & 0 & 1 \\ 
   & Founder died & 58 & 0.121 &   0.098 &   0.30 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 178 & 0.372 &   0.410 &   0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.211 &   0.189 &   0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.154 &   0.140 &   0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.263 &   0.261 &   0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 229 & 0.478 &   0.488 &   0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 &   0.304 &   0.46 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  &   0.797 &   0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  &   0.150 &   0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  &   0.054 &   0.23 & 0 & 1 \\ 
   & PC1 (Size) & 76.0366391388584 & 0.159 &   0.138 &   1.88 & -6.4 & 2.62 \\ 
   & PC2 (Support) & 58.6628793020593 & 0.122 &   0.179 &   1.49 & -5 & 2.74 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  &   0.411 &   1.23 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  &   1.322 &   1.69 & 0.000087 & 10.81 \\ 
   & Pop. (millions) country &  &  & 156.197 & 287.82 & 0.037 & 1412.36 \\ 
   & Nbr PM within 10km &  &  &   1.601 &   2.97 & 0 & 15 \\ 
   & PM density (10km) &  &  &   1.423 &   4.01 & 0 & 41.85 \\ 
   & Europe and North America & 312 & 0.651 &   0.645 &   0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 &   0.012 &   0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.267 &   0.282 &   0.45 & 0 & 1 \\ 
   & Region - Europe & 241 & 0.503 &   0.501 &   0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 &   0.042 &   0.20 & 0 & 1 \\ 
   & Region - North America & 71 & 0.148 &   0.143 &   0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 &   0.019 &   0.14 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

Overall the entire life span, the average hazard rate is 0.78\%, which allows comparison to other studies of NPO closure.
While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})

@@

Comparison to other forms of nonprofit organizations reported by \parencite{Gordon_etal_2013_insolvency}
places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.78\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
In fact, lower dissolution rates are only reported for historical societies (0.5\%) and libraries (0.2\%).

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon Apr 15 11:32:02 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .22 \; (0.37) \\ 
   & Gender - Couple & .14 \; (0.36) \\ 
   & Founder died & .28 \; (0.53) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .71 \; (0.48) \\ 
   & Self-Identification - Collection & .14 \; (0.59) \\ 
   & Self-Identification - Other & 1.32 \; (0.38)^{***} \\ 
   & AN Ranking - Included & .50 \; (0.38) \\ 
   & AN Ranking - Dropped & .82 \; (0.52) \\ 
   & Founder name in Museum name & -.35 \; (0.33) \\ 
   & MOW inclusion & -.90 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .56 \; (0.42) \\ 
   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
   & Pop. (millions) within 10km & .29 \; (0.11)^{**} \\ 
   & Nbr PM within 10km & .30 \; (0.09)^{***} \\ 
   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
   \hline
 & Museum-years & 6423 \\ 
   & Closures & 52 \\ 
   & log. Likelihood & -253.41 \\ 
   & AIC & 536.82 \\ 
   & BIC & 566.09 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

For this study, I only investigated the occurence of closure events.
However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms.
One way in which this can happen is when other parties, such as local governments other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
Sometimes this involves changes in the composition of the board of directors, with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum, often to an extent that it no longer fits the working definition.
Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was often not feasible to determine the date of such transitions\footnote{As a consequence of this, they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing. However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
Primarily this was due to the intransparency of these organizations, as well as the gradual process.
As the presence of non-founder members does not categorically exclude a museum from being categorized as private museum as long as third-party influence is limited, this influence can grow until the museum bears little resemblance to its former self.
The possibility of other outcomes than surival and closures has been investigated for NPOs more generally
\parencite{Searing_2020_zombies,HernandezOrtiz_2022_discontinuity,Helmig_Ingerfurth_Pinz_2013_nonprofit}, and for private museums specifically: 
\textcite{Walker_2019_collector} argues that in the case of Germany, private museum founders turn to the state to ensure the survival of their projects in the form of public-private partnerships.
Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research. 
\end{document}

>>>>

% Created 2024-04-22 ma 19:57
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

Investigating the survival prospects of private museum furthermore illucidates the long-term development of the organizational form as a whole.
While the composition of private museums is not only influenced by closures, but also by foundings, analysing the former provides insights in the sustainability of

Given the non-significant gender difference, it can be expected that (unless given a strong increase in founding by women) the population of private museums will continue to remain a dominated affair\footnote{The point estimates, which are higher for women and couples, albeit not significantly so, even point towards a slight expansion of the proportion of museums established by men.}
The role of the founder is two sided.
Death and exclusion from a prestigious ranking are not associated with a higher risk of closure, which indicates that private museums have attained a substantial degree of institutionalization.
On the other hand, self-identifying as an institution which is not a museum, foundation or collection possibly reflects a kind of founder attitudes which substantially influences survival chances.
Founders who are less interested in establish institutions might be more inclined to choose a name which less reflects this ambition. 
One way of conceptualizing this distinction might then be that whereas involuntary, externally imposed events are less able to close museums of otherwise motivated founders, some founders might from the very beginning voluntarily decide to not establish a museum that is intended for perpetuity.

However, this group is somewhat small.
Of the XXX museums included in the database, XXX do not carry the term museum, foundation or collection.
Thus given this low share, and the corresponding  higher closing rate, a possible future for the private museum population might be increased institutionalization and consolidation of relatively robust organizations.
The effects of location might be seen
On the one hand, museum location is chosen by the founder at the time of founding (or rather, several years in advance).
This gives founders substantial choice in the size and composition of the potential audience who will be able to easily assess the museum.
On the other hand, collectors are less able to influence what plans other collectors might have.
What may have been at one point been identified as a promising location without substantial competition may turn out to be a much less fertile ground as soon as other collectors start eyeing the same region for their own private museum projects.
In particular private museum in rural locations with low population densities seem to be at risk when other museums open in the neighborhood. 
This is not to say that private museums cannot endure in areas with low population densities. 
In fact, at low numbers of private museums in the neighborhood their survival prospects are better than those located in larger cities.
These larger cities with low private museum counts are possibly also characterized by lower numbers of other cultural institutions as well as an audience less interested in postmaterial art consumption.

The lack of a relation between temporary exhibitions and survival prospect is somewhat unexpected.
It was expected that as temporary exhibitions constitute one of the main tasks of a museums operations, organizing them would benefit a museum financially (via visitor fees) and symbolically (via prestige of other art field actors, which might be developed into further contacts), leading to higher survival chances\footnote{Furthermore, the ability to organization exhibitions likely reflects museum resources, which should also enhance survival.}
However, organizing exhibitions does not seem to bestow benefits for the museums which organize them, nor do organizations seem to be organized only by established/sustainable/secure organizations.
One possibility for this discrepancy could be that exhibitions are expensive, and whatever benefits gained from them are offset by the associated costs.
One might see in this association again the importance of the founder:
Founders who are committed to their museums will keep them alive, regardless of whether or not they plan to organize temporary exhibitions.

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Apr 19 19:04:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 274 & 0.573 & 5.9e-01 &   0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.159 & 1.7e-01 &   0.38 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.268 & 2.4e-01 &   0.43 & 0 & 1 \\ 
   & Founder died & 57 & 0.119 & 9.3e-02 &   0.29 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 177 & 0.370 & 4.0e-01 &   0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.211 & 1.9e-01 &   0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.155 & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.264 & 2.6e-01 &   0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 228 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 & 2.8e-01 &   0.45 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 8.0e-01 &   0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 1.5e-01 &   0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 5.6e-02 &   0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 6.5e-01 &   0.48 & 0 & 1 \\ 
   & Exhibition any last 5 years &  &  & 4.7e-01 &   0.50 & 0 & 1 \\ 
   & PC1 (Size) & 74.6913323980041 & 0.156 & 1.3e-01 &   1.88 & -6.4 & 2.62 \\ 
   & PC2 (Support) & 58.6876842646085 & 0.123 & 1.6e-01 &   1.50 & -5 & 2.74 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 4.3e-01 &   1.28 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.70 & 0.000087 & 10.81 \\ 
   & Pop. (millions) country &  &  & 1.6e+02 & 297.59 & 0.037 & 1412.36 \\ 
   & Nbr PM within 10km &  &  & 1.7e+00 &   3.07 & 0 & 15 \\ 
   & PM density (10km) &  &  & 1.5e+00 &   4.15 & 0 & 41.85 \\ 
   & Europe and North America & 311 & 0.651 & 6.5e-01 &   0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 & 1.2e-02 &   0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.268 & 2.8e-01 &   0.45 & 0 & 1 \\ 
   & Region - Europe & 241 & 0.504 & 5.1e-01 &   0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 & 4.4e-02 &   0.20 & 0 & 1 \\ 
   & Region - North America & 70 & 0.146 & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 & 1.9e-02 &   0.14 & 0 & 1 \\ 
   & year &  &  & 2.0e+03 &   5.75 & 2000 & 2021 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

Overall the entire life span, the average hazard rate is 0.77\%, which allows comparison to other studies of NPO closure.
While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})

@@

Comparison to other forms of nonprofit organizations reported by \parencite{Gordon_etal_2013_insolvency}
places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.77\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
In fact, lower dissolution rates are only reported for historical societies (0.5\%) and libraries (0.2\%).

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon Apr 22 19:37:32 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_wyr}\\ 
 \hline
  \multicolumn{4}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .16 \; (0.37) & .16 \; (0.37) \\ 
   & Gender - Couple & .20 \; (0.36) & .13 \; (0.37) \\ 
   & Founder died & -.06 \; (0.57) & -.02 \; (0.56) \\ 
   \multicolumn{4}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .93 \; (0.49) & .83 \; (0.48) \\ 
   & Self-Identification - Collection & .34 \; (0.59) & .36 \; (0.59) \\ 
   & Self-Identification - Other & 1.45 \; (0.39)^{***} & 1.38 \; (0.39)^{***} \\ 
   & AN Ranking - Included & .26 \; (0.38) & .22 \; (0.38) \\ 
   & AN Ranking - Dropped & .81 \; (0.51) & .66 \; (0.52) \\ 
   & Founder name in Museum name & -.44 \; (0.33) & -.42 \; (0.33) \\ 
   & Exhibition any & .13 \; (0.33) &  \\ 
   & Exhibition any last 5 years &  & .39 \; (0.32) \\ 
   \multicolumn{4}{l}{\textbf{Environment}} \\ 
 & Time Period 2005-2009 &  & .40 \; (1.16) \\ 
   & Time Period 2010-2014 &  & 1.28 \; (1.04) \\ 
   & Time Period 2015-2019 &  & 1.43 \; (1.03) \\ 
   & Time Period 2020-2024 &  & 1.51 \; (1.05) \\ 
   & PM density (country) & .63 \; (0.45) & .52 \; (0.51) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) \\ 
   & Pop. (millions) within 10km & .32 \; (0.11)^{**} & .30 \; (0.12)^{**} \\ 
   & Nbr PM within 10km & .29 \; (0.09)^{**} & .26 \; (0.09)^{**} \\ 
   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} & -.09 \; (0.04)^{**} \\ 
   \hline
 & Museum-years & 5862 & 5862 \\ 
   & Closures & 51 & 51 \\ 
   & log. Likelihood & -246.02 & -241.64 \\ 
   & AIC & 522.03 & 521.28 \\ 
   & BIC & 551.01 & 557.99 \\ 
   \hline 
 \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

For this study, I only investigated the occurence of closure events.
However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms.
One way in which this can happen is when other parties, such as local governments other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
Sometimes this involves changes in the composition of the board of directors, with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum, often to an extent that it no longer fits the working definition.
Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was often not feasible to determine the date of such transitions\footnote{As a consequence of this, they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing. However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
Primarily this was due to the intransparency of these organizations, as well as the gradual process.
As the presence of non-founder members does not categorically exclude a museum from being categorized as private museum as long as third-party influence is limited, this influence can grow until the museum bears little resemblance to its former self.
The possibility of other outcomes than surival and closures has been investigated for NPOs more generally
\parencite{Searing_2020_zombies,HernandezOrtiz_2022_discontinuity,Helmig_Ingerfurth_Pinz_2013_nonprofit}, and for private museums specifically: 
\textcite{Walker_2019_collector} argues that in the case of Germany, private museum founders turn to the state to ensure the survival of their projects in the form of public-private partnerships.
Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research.

environment can be measured more
\begin{itemize}
\item geocoding of other institutiosn
\item tax incentives
\item government spending
\end{itemize}
-> this might futher specify the niches in which PMs can endure
\end{document}
